Validation of marker gene expression

### 2025-07-03 analyses/cell-type-consensus/template-notebooks/marker-gene-validation.Rmd

# path to results directory
results_dir <- file.path(module_base, "..", "..", "data", "current", "results", "cell-type-consensus", params$project_id)
```

@@

# check that consensus results exist
stopifnot(
  "No cell type results found in data/current/results/cell-type-consensus" = length(consensus_results_files) > 0,
  "No gene expression files found in data/current/results/cell-type-consensus" = length(gene_exp_files) > 0
)
```

@@

# now only keep unique markers for the dotplot 
unique_markers_df <- filtered_markers_df |> 
  dplyr::filter(gene_observed_count == 1 | validation_group_annotation == "hematopoietic precursor cell")

>>>>

# path to the `2025-03-20` release results directory
results_dir <- file.path(module_base, "..", "..", "data", "2025-03-20", "results", "cell-type-consensus", params$project_id)
```

@@

# check that consensus results exist
stopifnot(
  "No cell type results found in data/2025-03-20/results/cell-type-consensus. Please make sure you downloaded result files with the flag `--release 2025-03-20`." = length(consensus_results_files) > 0,
  "No gene expression files found in data/2025-03-20/results/cell-type-consensus. Please make sure you downloaded result files with the flag `--release 2025-03-20`." = length(gene_exp_files) > 0
)
```

@@

# now only keep unique markers for the dotplot
# except for hematopoietic precursor cells, where there are no unique markers
unique_markers_df <- filtered_markers_df |>
  dplyr::filter(gene_observed_count == 1 | validation_group_annotation == "hematopoietic precursor cell")
